---
title: 'French lexicon project: ex-Gaussian fits'
author: "Guillaume A. Rousselet"
date: "`r Sys.Date()`"
output:
  pdf_document:
    fig_caption: no
    number_sections: no
    toc: yes
    toc_depth: 2
---

```{r message=FALSE}
# dependencies
library(ggplot2)
library(cowplot)
library(tibble)
library(retimes)
library(HDInterval)
```

```{r}
sessionInfo()
```

# Lexical decision dataset

Data from the [French Lexicon Project](https://sites.google.com/site/frenchlexicon/results).
Click on "French Lexicon Project trial-level results with R scripts.zip".
The `.RData` dataset was created by applying the script `/code/getflprtdata.Rmd`.

```{r}
# get data - tibble = `flp`
load("./data/french_lexicon_project_rt_data.RData")
# columns =
#1 = participant
#2 = rt
#3 = acc = accuracy 0/1
#4 = condition = word/non-word
p.list <- unique(flp$participant)
Np <- length(p.list)
exg_param_w <- matrix(ncol=3, nrow=Np)
exg_param_nw <- matrix(ncol=3, nrow=Np)
```

N = `r length(unique(flp$participant))` participants.

# Check ex Gaussian fit

Word / non-word comparison:
```{r eval=TRUE}
# select participant
p.list <- unique(flp$participant)
sp <- p.list[1]

# make KDE
flp.w <- sort(flp$rt[flp$participant==sp & flp$condition=="word"])
flp.nw <- sort(flp$rt[flp$participant==sp & flp$condition=="non-word"])
out <- timefit(flp.w, plot = TRUE)
```

```{r}
out <- timefit(flp.nw, plot = TRUE)
```

## Get distribution of parameters by resampling

```{r}
out <- timefit(flp.w, plot = TRUE, iter = 100)
```

```{r}
out <- timefit(flp.nw, plot = TRUE, iter = 100)
```

# Get parameters for all participants

```{r eval=FALSE}
for(P in 1:Np){
  # Word
  flp.w <- sort(flp$rt[flp$participant==p.list[P] & flp$condition=="word"])
  out <- timefit(flp.w)
  exg_param_w[P,] <- out@par
  
  # Non-Word
  flp.nw <- sort(flp$rt[flp$participant==p.list[P] & flp$condition=="non-word"])
  out <- timefit(flp.nw)
  exg_param_nw[P,] <- out@par
}

colnames(exg_param_w) <- c("mu", "sigma", "tau")
colnames(exg_param_nw) <- c("mu", "sigma", "tau")

save(exg_param_w,
     exg_param_nw,
     file = './data/flp_exg_param.RData')
```

# Illustrate parameters

```{r}
load('./data/flp_exg_param.RData')

# create data frame
df <- tibble(values = c(as.vector(exg_param_w),as.vector(exg_param_nw)),
             Condition = c(rep("Word", Np*3), rep("Non-Word", Np*3)),
             Parameter = rep(rep(c("Mu", "Sigma", "Tau"), each = Np),2)
             )

# make plot
ggplot(df, aes(x = values)) + theme_classic() +
  geom_density() +
  facet_grid(rows = vars(Condition), cols = vars(Parameter), scales = "free_x")
```

# Compare parameters

## Mu
```{r}
params <- c("Mu", "Sigma", "Tau")
paste("Word","Non-Word","Difference")
P <- 1
hdires <- round(hdi(exg_param_nw[,P]-exg_param_w[,P],credMass=0.80))
paste0(params[P],": ",round(median(exg_param_w[,P])),", ",
  round(median(exg_param_nw[,P])),", ",            round(median(exg_param_nw[,P])-median(exg_param_w[,P]))," [",
            hdires[1],", ", hdires[2],"]")
```

```{r}
plot(exg_param_w[,P],exg_param_nw[,P], 
     xlab = paste0(params[P],": Word"),
     ylab = paste0(params[P],": Non-Word"))
abline(a = 0, b = 1)
```

## Sigma
```{r}
P <- 2
hdires <- round(hdi(exg_param_nw[,P]-exg_param_w[,P],credMass=0.80))
paste0(params[P],": ",round(median(exg_param_w[,P])),", ",
  round(median(exg_param_nw[,P])),", ",            round(median(exg_param_nw[,P])-median(exg_param_w[,P]))," [",
            hdires[1],", ", hdires[2],"]")
```

```{r}
plot(exg_param_w[,P],exg_param_nw[,P], 
     xlab = paste0(params[P],": Word"),
     ylab = paste0(params[P],": Non-Word"))
abline(a = 0, b = 1)
```

## Tau
```{r}
P <- 3
hdires <- round(hdi(exg_param_nw[,P]-exg_param_w[,P],credMass=0.80))
paste0(params[P],": ",round(median(exg_param_w[,P])),", ",
  round(median(exg_param_nw[,P])),", ",            round(median(exg_param_nw[,P])-median(exg_param_w[,P]))," [",
            hdires[1],", ", hdires[2],"]")
```

```{r}
plot(exg_param_w[,P],exg_param_nw[,P], 
     xlab = paste0(params[P],": Word"),
     ylab = paste0(params[P],": Non-Word"))
abline(a = 0, b = 1)
```


## Parameter correlations: Word

```{r}
pairs(exg_param_w)
```
## Parameter correlations: Non-Word

```{r}
pairs(exg_param_nw)
```

# Covariance matrices

```{r}
# covmat_w <- cov(exg_param_w)
cov(exg_param_w)
```

```{r}
# covmat_nw <- cov(exg_param_nw)
cov(exg_param_nw)
```

# Correlation matrices

```{r}
# covmat_w <- cov(exg_param_w)
cov2cor(cov(exg_param_w))
```

```{r}
# covmat_nw <- cov(exg_param_nw)
cov2cor(cov(exg_param_nw))
```

# ExG fit of ExG parameters

## Word

### Mu
```{r}
exg_param_w_meta <- list()
exg_param_nw_meta <- list()

out <- timefit(exg_param_w[,1], plot = TRUE)
out@par
exg_param_w_meta$mu <- out@par
```

### Sigma
```{r}
out <- timefit(exg_param_w[,2], plot = TRUE)
out@par
exg_param_w_meta$sigma <- out@par
```

### Tau
```{r}
out <- timefit(exg_param_w[,3], plot = TRUE)
out@par
exg_param_w_meta$tau <- out@par
```

## Non-Word

### Mu
```{r}
out <- timefit(exg_param_nw[,1], plot = TRUE)
out@par
exg_param_nw_meta$mu <- out@par
```

### Sigma
```{r}
out <- timefit(exg_param_nw[,2], plot = TRUE)
out@par
exg_param_nw_meta$sigma <- out@par
```

### Tau
```{r}
out <- timefit(exg_param_nw[,3], plot = TRUE)
out@par
exg_param_nw_meta$tau <- out@par
```

```{r}
save(exg_param_w,
     exg_param_nw,
     exg_param_w_meta,
     exg_param_nw_meta,
     file = './data/flp_exg_param.RData')
```

# Simulate RT distributions using exG parameters

## Sample participants' parameters with replacement

```{r}
Np.total <- nrow(exg_param_w)
Np <- 20 # participants
Nt <- 100 # trials
rt_data <- matrix(ncol=Np, nrow=Nt)

# Resample participants' triads
bootsample <- sample(Np.total, Np, replace = TRUE)

# Generate random trials for each participant
# based on their triads of ex Gaussian parameters
for(P in 1:Np){
  rt_data[,P] <- rexgauss(Nt, 
                     mu = exg_param_w[bootsample[P],1], 
                     sigma = exg_param_w[bootsample[P],2], 
                     tau = exg_param_w[bootsample[P],3])
}

```

## Illustrate results
```{r}
df <- tibble(rt = as.vector(rt_data),
             Participant = factor(rep(seq(1,Np),each = Nt)))

ggplot(df, aes(x = rt, colour = Participant)) + 
  geom_density()
```

