---
title: "Quantile estimation bias: Harrell-Davis and quantile(type=8)"
author: "Guillaume A. Rousselet"
date: "`r Sys.Date()`"
output:
  pdf_document:
    fig_caption: no
    number_sections: no
    toc: yes
    toc_depth: 2
---

```{r message=FALSE, warning=FALSE}
# dependencies
# install.packages("devtools")
# devtools::install_github("GRousselet/rogme")
library(rogme)
library(tibble)
library(tidyr)
library(cowplot)
library(retimes)
source("./functions/gh.txt")
source("./functions/akerd.txt")
source("./functions/skew.txt")
library(beepr)
```

```{r}
sessionInfo()
```

Goal: to illustrate bias of quantiles using g & h distributions and Miller's 12 ex-Gaussian distributions. We limit our investigation to deciles, estimated using `hd()` and `quantile(type = 8)`.

The `quantile` function in base R offers 9 options. Option 8 was recommended by Hyndman and Fan (1996). It gives quantile estimates that are approximately median-unbiased regardless of the distribution of x. Preliminary tests suggest weaker bias for the extreme deciles compared to the Harrell-Davis quantile estimator. If this is the case, should be tested in `sim_gp_fp` in the hierarchical context. 

# g & h distributions

The ghdist() function is used to generate random numbers from g & h distributions. All such distributions have a median of zero. The parameter g controls the asymmetry of the distribution, while the parameter h controls the thickness of the tails. The g & h distributions are described in this 1985 book:
http://eu.wiley.com/WileyCDA/WileyTitle/productCd-047004005X.html
There is also a description in Rand Wilcox's book Introduction to Robust Estimation.

## Estimate population parameters from large samples

```{r}
set.seed(4)

gvec <- seq(0, 1, 0.1) # g values
pop.hd <- matrix(NA, nrow = length(gvec), ncol = 9)
pop.q <- matrix(NA, nrow = length(gvec), ncol = 9)
pop.skew <- matrix(NA, nrow = length(gvec), ncol = 1)
pop.kurt <- matrix(NA, nrow = length(gvec), ncol = 1)
n <- 1000000

for(G in 1:length(gvec)){
  pop <- sort(ghdist(n, g = gvec[G], h = 0))
  pop.hd[G,] <- hdseq(pop)
  for(D in 1:9){
  pop.q[G,D] <- pop[round(n*D/10)] # population deciles
  }
  pop.skew[G] <- skew(pop) 
  pop.kurt[G] <- kurt(pop) 
}
```

## Population HD
```{r}
round(pop.hd, digits = 2)
```

## Population deciles
```{r}
round(pop.q, digits = 2)
```

## Population skewness
```{r}
pop.skew
```

## Population kurtosis
```{r}
pop.kurt
```

## Simulation 

```{r eval=FALSE}
gvec <- seq(0, 1, 0.1) # g values
nvec <- c(seq(30,100,10), 150, 200, 300) # vector of sample sizes to test
nsim <- 10000 # simulation samples
nboot <- 200 # samples for bias correction
prob.seq <- seq(0.1, 0.9, 0.1) # input to quantile function
q.type <- 8 # quantile type input - type 8 recommended by Hyndman and Fan (1996) - quantile estimates approximately median-unbiased regardless of the distribution of x.

# declare matrices of results - save all iterations
sim.hd.bias <- array(NA, dim = c(nsim, length(gvec), length(nvec), 9))
sim.hd.bc <- array(NA, dim = c(nsim, length(gvec), length(nvec), 9))
boot.hd <- array(NA, dim = c(nboot, 9))
sim.q.bias <- array(NA, dim = c(nsim, length(gvec), length(nvec), 9))
sim.q.bc <- array(NA, dim = c(nsim, length(gvec), length(nvec), 9))
boot.q <- array(NA, dim = c(nboot, 9))

set.seed(21)
beep(3)

for(S in 1:nsim){ # simulation iterations
  
  if(S %% 500 == 0){
    print(paste0("HD bias: simulation ",S," out of ",nsim,"..."))
    beep(2)
  }
  
  for(G in 1:length(gvec)){
    
    large.sample <- ghdist(max(nvec), g = gvec[G], h = 0)  
    
    for(N in 1:length(nvec)){ # sample sizes
      
      current.sample <- large.sample[1:nvec[N]]
      
      sim.hd.bias[S,G,N,] <- hdseq(current.sample)
      sim.q.bias[S,G,N,] <- quantile(current.sample, probs = prob.seq, type = 8)
      
      for(b in 1:nboot){
        boot.hd[b,] <- hdseq(sample(current.sample, nvec[N], replace = TRUE))
        boot.q[b,] <- quantile(sample(current.sample, nvec[N], replace = TRUE), 
                               probs = prob.seq, type = 8)
      }
      sim.hd.bc[S,G,N,] <- 2*sim.hd.bias[S,G,N,] - apply(boot.hd, 2, mean) - pop.q[G,]
      sim.q.bc[S,G,N,] <- 2*sim.q.bias[S,G,N,] - apply(boot.q, 2, mean) - pop.q[G,]
      
      sim.hd.bias[S,G,N,] <- sim.hd.bias[S,G,N,] - pop.q[G,]
      sim.q.bias[S,G,N,] <- sim.q.bias[S,G,N,] - pop.q[G,]
      
    }
  }
}
save(
  sim.hd.bias,
  sim.q.bias,
  sim.hd.bc,
  sim.q.bc,
  gvec,
  nvec,
  nsim,
  file=paste0('./data/sim_hd_bias.RData'))
beep(8)
```

## Compute bias
Bias = average of sample estimates minus population value (already subtracted during simulation).

```{r}
load('./data/sim_hd_bias.RData')

bias.hd <- apply(sim.hd.bias, c(2,3,4), mean, na.rm = TRUE)
bias.hd.md <- apply(sim.hd.bias, c(2,3,4), median, na.rm = TRUE)
bias.hd.bc <- apply(sim.hd.bc, c(2,3,4), mean, na.rm = TRUE)

bias.q <- apply(sim.q.bias, c(2,3,4), mean, na.rm = TRUE)
bias.q.md <- apply(sim.q.bias, c(2,3,4), median, na.rm = TRUE)
bias.q.bc <- apply(sim.q.bc, c(2,3,4), mean, na.rm = TRUE)

x.labels <- c("30","","50","","70","","90","", "150", "200", "300")
```

## Illustrate bias results

### Make function
```{r}
plot_bias_res <- function(data, gvec, nvec, x.labels){
df <- tibble(Bias = as.vector(data),
             g = factor(rep(gvec, length(nvec)*9)),
             Size = rep(rep(nvec,each=length(gvec)), 9),
             q = factor(rep(seq(1,9), each=length(gvec)*length(nvec))))

# make plot
p <- ggplot(df) + theme_classic() +
  geom_line(aes(x=Size, y=Bias, colour = g), size = 1) + 
  geom_abline(intercept=0, slope=0, colour="black") +
  scale_colour_viridis_d() +
  scale_x_continuous(breaks=nvec, labels = x.labels) +
  scale_y_continuous(breaks=seq(0,0.6,0.2)) +
  coord_cartesian(ylim=c(-0.1,0.7)) +
  theme(plot.title = element_text(size=22),
        axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 14, colour="black"),
        axis.text.y = element_text(size = 16, colour="black"),
        axis.title.y = element_text(size = 18),
        legend.key.width = unit(1.5,"cm"),
        legend.position = "right",
        # legend.position = c(0.55,0.85),
        legend.direction = "vertical",
        legend.text=element_text(size=16),
        legend.title=element_text(size=18),
        strip.background=element_rect(fill="grey", colour="black"),
        strip.text=element_text(size=16, colour="white", face="bold")) +
  labs(x = "Sample size", y = "Bias") +
  # make thicker legend lines
  guides(colour = guide_legend(override.aes = list(size=3))) +
  facet_wrap( ~ q, ncol = 3)
p
}
```

```{r, fig.width = 12, fig.height = 7}
p <- plot_bias_res(bias.hd, gvec, nvec, x.labels)
p <- p + ggtitle("HD mean bias") 
p
```

```{r, fig.width = 12, fig.height = 7}
p <- plot_bias_res(bias.q, gvec, nvec, x.labels)
p <- p + ggtitle("QT8 mean bias") 
p
```

## Illustrate median bias results

```{r, fig.width = 12, fig.height = 7}
p <- plot_bias_res(bias.hd.md, gvec, nvec, x.labels)
p <- p + ggtitle("HD median bias") 
p
```

```{r, fig.width = 12, fig.height = 7}
p <- plot_bias_res(bias.q.md, gvec, nvec, x.labels)
p <- p + ggtitle("QT8 median bias") 
p
```

## Illustrate bias corrected bias results

```{r, fig.width = 12, fig.height = 7}
p <- plot_bias_res(bias.hd.bc, gvec, nvec, x.labels)
p <- p + ggtitle("HD mean bias (BC)") 
p
```

```{r, fig.width = 12, fig.height = 7}
p <- plot_bias_res(bias.q.bc, gvec, nvec, x.labels)
p <- p + ggtitle("QT8 mean bias (BC)") 
p
```

## Illustrate sampling distributions: HD

### Sample size = 30, q = 1

```{r}
# fig.width = 10, fig.height = 6
df <- tibble(Difference = as.vector(sim.hd.bias[,,1,1]),
             g = factor(rep(gvec, each = nsim))
             )

# make plot
p <- ggplot(df, aes(x = Difference, colour = g)) + theme_classic() +
  geom_density() +
  scale_colour_viridis_d() +
  scale_x_continuous(breaks=nvec, labels = x.labels) +
  # scale_y_continuous(breaks=c(-5,seq(0,50,10))) +
  coord_cartesian(xlim=c(-2.5,2.5)) +
  theme(plot.title = element_text(size=22),
        axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 14, colour="black"),
        axis.text.y = element_text(size = 16, colour="black"),
        axis.title.y = element_text(size = 18),
        legend.key.width = unit(1.5,"cm"),
        legend.position = "right", #c(0.85,0.65),
        legend.text=element_text(size=16),
        legend.title=element_text(size=18)) +
  # labs(x = "Sample size", y = "Bias in ms") +
  # make thicker legend lines
  guides(colour = guide_legend(override.aes = list(size=3)))
 # + ggtitle("Median RT") 
p
# save figure
# ggsave(filename=paste0('figure_miller_bias_md.pdf'),width=10,height=6) 
```

### Sample size = 30, q = 5

```{r}
# fig.width = 10, fig.height = 6
df <- tibble(Difference = as.vector(sim.hd.bias[,,1,5]),
             g = factor(rep(gvec, each = nsim))
             )

# make plot
p <- ggplot(df, aes(x = Difference, colour = g)) + theme_classic() +
  geom_density() +
  scale_colour_viridis_d() +
  scale_x_continuous(breaks=nvec, labels = x.labels) +
  # scale_y_continuous(breaks=c(-5,seq(0,50,10))) +
  coord_cartesian(xlim=c(-2.5,2.5)) +
  theme(plot.title = element_text(size=22),
        axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 14, colour="black"),
        axis.text.y = element_text(size = 16, colour="black"),
        axis.title.y = element_text(size = 18),
        legend.key.width = unit(1.5,"cm"),
        legend.position = "right", #c(0.85,0.65),
        legend.text=element_text(size=16),
        legend.title=element_text(size=18)) +
  # labs(x = "Sample size", y = "Bias in ms") +
  # make thicker legend lines
  guides(colour = guide_legend(override.aes = list(size=3)))
 # + ggtitle("Median RT") 
p
# save figure
# ggsave(filename=paste0('figure_miller_bias_md.pdf'),width=10,height=6) 
```

### Sample size = 30, q = 9

```{r}
# fig.width = 10, fig.height = 6
df <- tibble(Difference = as.vector(sim.hd.bias[,,1,9]),
             g = factor(rep(gvec, each = nsim))
             )

# make plot
p <- ggplot(df, aes(x = Difference, colour = g)) + theme_classic() +
  geom_density() +
  scale_colour_viridis_d() +
  scale_x_continuous(breaks=nvec, labels = x.labels) +
  # scale_y_continuous(breaks=c(-5,seq(0,50,10))) +
  coord_cartesian(xlim=c(-2.5,2.5)) +
  theme(plot.title = element_text(size=22),
        axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 14, colour="black"),
        axis.text.y = element_text(size = 16, colour="black"),
        axis.title.y = element_text(size = 18),
        legend.key.width = unit(1.5,"cm"),
        legend.position = "right", #c(0.85,0.65),
        legend.text=element_text(size=16),
        legend.title=element_text(size=18)) +
  # labs(x = "Sample size", y = "Bias in ms") +
  # make thicker legend lines
  guides(colour = guide_legend(override.aes = list(size=3)))
 # + ggtitle("Median RT") 
p
# save figure
# ggsave(filename=paste0('figure_miller_bias_md.pdf'),width=10,height=6) 
```

### Sample size = 30

```{r}
# fig.width = 10, fig.height = 6
df <- tibble(Difference = as.vector(sim.hd.bias[,,1,]),
             g = factor(rep(rep(gvec, each = nsim),9)),
             q = factor(rep(seq(1,9), each = nsim*length(gvec)))
             )

# make plot
p <- ggplot(df, aes(x = Difference, colour = g)) + theme_classic() +
  geom_density() +
  scale_colour_viridis_d() +
  scale_x_continuous(breaks=nvec, labels = x.labels) +
  # scale_y_continuous(breaks=c(-5,seq(0,50,10))) +
  coord_cartesian(xlim=c(-2.5,2.5)) +
  theme(plot.title = element_text(size=22),
        axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 14, colour="black"),
        axis.text.y = element_text(size = 16, colour="black"),
        axis.title.y = element_text(size = 18),
        legend.key.width = unit(1.5,"cm"),
        legend.position = "right", #c(0.85,0.65),
        legend.text=element_text(size=16),
        legend.title=element_text(size=18),
        strip.background=element_rect(fill="grey", colour="black"),
        strip.text=element_text(size=16, colour="white", face="bold")) +
  # labs(x = "Sample size", y = "Bias in ms") +
  # make thicker legend lines
  guides(colour = guide_legend(override.aes = list(size=3))) +
 facet_wrap( ~ q, ncol = 3)
 # + ggtitle("Median RT") 
p
# save figure
# ggsave(filename=paste0('figure_miller_bias_md.pdf'),width=10,height=6) 
```

### Sample size = 300

```{r}
# fig.width = 10, fig.height = 6
df <- tibble(Difference = as.vector(sim.hd.bias[,,11,]),
             g = factor(rep(rep(gvec, each = nsim),9)),
             q = factor(rep(seq(1,9), each = nsim*length(gvec)))
             )

# make plot
p <- ggplot(df, aes(x = Difference, colour = g)) + theme_classic() +
  geom_density() +
  scale_colour_viridis_d() +
  scale_x_continuous(breaks=nvec, labels = x.labels) +
  # scale_y_continuous(breaks=c(-5,seq(0,50,10))) +
  coord_cartesian(xlim=c(-1,1)) +
  theme(plot.title = element_text(size=22),
        axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 14, colour="black"),
        axis.text.y = element_text(size = 16, colour="black"),
        axis.title.y = element_text(size = 18),
        legend.key.width = unit(1.5,"cm"),
        legend.position = "right", #c(0.85,0.65),
        legend.text=element_text(size=16),
        legend.title=element_text(size=18),
        strip.background=element_rect(fill="grey", colour="black"),
        strip.text=element_text(size=16, colour="white", face="bold")) +
  # labs(x = "Sample size", y = "Bias in ms") +
  # make thicker legend lines
  guides(colour = guide_legend(override.aes = list(size=3))) +
 facet_wrap( ~ q, ncol = 3)
 # + ggtitle("Median RT") 
p
```

## Illustrate sampling distributions: QT8

### Sample size = 30, q = 1

```{r}
# fig.width = 10, fig.height = 6
df <- tibble(Difference = as.vector(sim.q.bias[,,1,1]),
             g = factor(rep(gvec, each = nsim))
             )

# make plot
p <- ggplot(df, aes(x = Difference, colour = g)) + theme_classic() +
  geom_density() +
  scale_colour_viridis_d() +
  scale_x_continuous(breaks=nvec, labels = x.labels) +
  # scale_y_continuous(breaks=c(-5,seq(0,50,10))) +
  coord_cartesian(xlim=c(-2.5,2.5)) +
  theme(plot.title = element_text(size=22),
        axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 14, colour="black"),
        axis.text.y = element_text(size = 16, colour="black"),
        axis.title.y = element_text(size = 18),
        legend.key.width = unit(1.5,"cm"),
        legend.position = "right", #c(0.85,0.65),
        legend.text=element_text(size=16),
        legend.title=element_text(size=18)) +
  # labs(x = "Sample size", y = "Bias in ms") +
  # make thicker legend lines
  guides(colour = guide_legend(override.aes = list(size=3)))
 # + ggtitle("Median RT") 
p
# save figure
# ggsave(filename=paste0('figure_miller_bias_md.pdf'),width=10,height=6) 
```

### Sample size = 30, q = 5

```{r}
# fig.width = 10, fig.height = 6
df <- tibble(Difference = as.vector(sim.q.bias[,,1,5]),
             g = factor(rep(gvec, each = nsim))
             )

# make plot
p <- ggplot(df, aes(x = Difference, colour = g)) + theme_classic() +
  geom_density() +
  scale_colour_viridis_d() +
  scale_x_continuous(breaks=nvec, labels = x.labels) +
  # scale_y_continuous(breaks=c(-5,seq(0,50,10))) +
  coord_cartesian(xlim=c(-2.5,2.5)) +
  theme(plot.title = element_text(size=22),
        axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 14, colour="black"),
        axis.text.y = element_text(size = 16, colour="black"),
        axis.title.y = element_text(size = 18),
        legend.key.width = unit(1.5,"cm"),
        legend.position = "right", #c(0.85,0.65),
        legend.text=element_text(size=16),
        legend.title=element_text(size=18)) +
  # labs(x = "Sample size", y = "Bias in ms") +
  # make thicker legend lines
  guides(colour = guide_legend(override.aes = list(size=3)))
 # + ggtitle("Median RT") 
p
```

### Sample size = 30, q = 9

```{r}
# fig.width = 10, fig.height = 6
df <- tibble(Difference = as.vector(sim.q.bias[,,1,9]),
             g = factor(rep(gvec, each = nsim))
             )

# make plot
p <- ggplot(df, aes(x = Difference, colour = g)) + theme_classic() +
  geom_density() +
  scale_colour_viridis_d() +
  scale_x_continuous(breaks=nvec, labels = x.labels) +
  # scale_y_continuous(breaks=c(-5,seq(0,50,10))) +
  coord_cartesian(xlim=c(-2.5,2.5)) +
  theme(plot.title = element_text(size=22),
        axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 14, colour="black"),
        axis.text.y = element_text(size = 16, colour="black"),
        axis.title.y = element_text(size = 18),
        legend.key.width = unit(1.5,"cm"),
        legend.position = "right", #c(0.85,0.65),
        legend.text=element_text(size=16),
        legend.title=element_text(size=18)) +
  # labs(x = "Sample size", y = "Bias in ms") +
  # make thicker legend lines
  guides(colour = guide_legend(override.aes = list(size=3)))
 # + ggtitle("Median RT") 
p
```

### Sample size = 30

```{r}
# fig.width = 10, fig.height = 6
df <- tibble(Difference = as.vector(sim.q.bias[,,1,]),
             g = factor(rep(rep(gvec, each = nsim),9)),
             q = factor(rep(seq(1,9), each = nsim*length(gvec)))
             )

# make plot
p <- ggplot(df, aes(x = Difference, colour = g)) + theme_classic() +
  geom_density() +
  scale_colour_viridis_d() +
  scale_x_continuous(breaks=nvec, labels = x.labels) +
  # scale_y_continuous(breaks=c(-5,seq(0,50,10))) +
  coord_cartesian(xlim=c(-2.5,2.5)) +
  theme(plot.title = element_text(size=22),
        axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 14, colour="black"),
        axis.text.y = element_text(size = 16, colour="black"),
        axis.title.y = element_text(size = 18),
        legend.key.width = unit(1.5,"cm"),
        legend.position = "right", #c(0.85,0.65),
        legend.text=element_text(size=16),
        legend.title=element_text(size=18),
        strip.background=element_rect(fill="grey", colour="black"),
        strip.text=element_text(size=16, colour="white", face="bold")) +
  # labs(x = "Sample size", y = "Bias in ms") +
  # make thicker legend lines
  guides(colour = guide_legend(override.aes = list(size=3))) +
 facet_wrap( ~ q, ncol = 3)
 # + ggtitle("Median RT") 
p
```

### Sample size = 300

```{r}
# fig.width = 10, fig.height = 6
df <- tibble(Difference = as.vector(sim.q.bias[,,11,]),
             g = factor(rep(rep(gvec, each = nsim),9)),
             q = factor(rep(seq(1,9), each = nsim*length(gvec)))
             )

# make plot
p <- ggplot(df, aes(x = Difference, colour = g)) + theme_classic() +
  geom_density() +
  scale_colour_viridis_d() +
  scale_x_continuous(breaks=nvec, labels = x.labels) +
  # scale_y_continuous(breaks=c(-5,seq(0,50,10))) +
  coord_cartesian(xlim=c(-1,1)) +
  theme(plot.title = element_text(size=22),
        axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 14, colour="black"),
        axis.text.y = element_text(size = 16, colour="black"),
        axis.title.y = element_text(size = 18),
        legend.key.width = unit(1.5,"cm"),
        legend.position = "right", #c(0.85,0.65),
        legend.text=element_text(size=16),
        legend.title=element_text(size=18),
        strip.background=element_rect(fill="grey", colour="black"),
        strip.text=element_text(size=16, colour="white", face="bold")) +
  # labs(x = "Sample size", y = "Bias in ms") +
  # make thicker legend lines
  guides(colour = guide_legend(override.aes = list(size=3))) +
 facet_wrap( ~ q, ncol = 3)
 # + ggtitle("Median RT") 
p
```

# Ex-Gaussian distributions

## Define Miller's ex-Gaussian parameters 
```{r}
load('./data/miller_exg_param.RData')
```

## Population HD
```{r}
round(pop.hd)
```

## Population deciles
```{r}
round(pop.q)
```

## Population skewness
```{r}
pop.skew
```

## Population kurtosis
```{r}
pop.kurt
```

## Simulation 

```{r eval=FALSE}
nvec <- c(seq(30,100,10), 150, 200, 300) # vector of sample sizes to test
nsim <- 10000 # simulation samples
nboot <- 200 # samples for bias correction
prob.seq <- seq(0.1, 0.9, 0.1) # input to quantile function
q.type <- 8 # quantile type input - type 8 recommended by Hyndman and Fan (1996) - quantile estimates approximately median-unbiased regardless of the distribution of x.

# declare matrices of results - save all iterations
sim.hd.bias <- array(NA, dim = c(nsim, nP, length(nvec), 9))
sim.hd.bc <- array(NA, dim = c(nsim, nP, length(nvec), 9))
boot.hd <- array(NA, dim = c(nboot, 9))
sim.q.bias <- array(NA, dim = c(nsim, nP, length(nvec), 9))
sim.q.bc <- array(NA, dim = c(nsim, nP, length(nvec), 9))
boot.q <- array(NA, dim = c(nboot, 9))

set.seed(21)
beep(3)

for(S in 1:nsim){ # simulation iterations
  
  if(S == 1){beep(2)}
  if(S %% 500 == 0){
    print(paste0("HD bias: simulation ",S," out of ",nsim,"..."))
    beep(2)
  }
  
  for(P in 1:nP){ # ex-Gaussian parameters
    
    mu <- miller.param[P,1]
    sigma <- miller.param[P,2]
    tau <- miller.param[P,3]
    large.sample <- rexgauss(max(nvec), mu = mu, sigma = sigma, tau = tau)  
    
    for(N in 1:length(nvec)){ # sample sizes
      
      current.sample <- large.sample[1:nvec[N]]
      sim.hd.bias[S,P,N,] <- hdseq(current.sample) 
      sim.q.bias[S,P,N,] <- quantile(current.sample, probs = prob.seq, type = 8)
      
      for(b in 1:nboot){
        boot.hd[b,] <- hdseq(sample(current.sample, nvec[N], replace = TRUE))
        boot.q[b,] <- quantile(sample(current.sample, nvec[N], replace = TRUE), 
                               probs = prob.seq, type = 8)
      }
      sim.hd.bc[S,P,N,] <- 2*sim.hd.bias[S,P,N,] - apply(boot.hd, 2, mean) - pop.q[P,]
      sim.q.bc[S,P,N,] <- 2*sim.q.bias[S,P,N,] - apply(boot.q, 2, mean) - pop.q[P,]
      
      sim.hd.bias[S,P,N,] <- sim.hd.bias[S,P,N,] - pop.q[P,]
      sim.q.bias[S,P,N,] <- sim.q.bias[S,P,N,] - pop.q[P,]
    }
  }
}
save(
  sim.hd.bias,
  sim.hd.bc,
  sim.q.bias,
  sim.q.bc,
  gvec,
  nvec,
  nsim,
  file=paste0('./data/sim_hd_bias_exg.RData'))
beep(8)
```

## Compute bias
Bias = average of sample estimates minus population value (already subtracted during simulation).

```{r}
load('./data/sim_hd_bias_exg.RData')
bias.hd <- apply(sim.hd.bias, c(2,3,4), mean, na.rm = TRUE)
bias.hd.md <- apply(sim.hd.bias, c(2,3,4), median, na.rm = TRUE)
bias.hd.bc <- apply(sim.hd.bc, c(2,3,4), mean, na.rm = TRUE)

bias.q <- apply(sim.q.bias, c(2,3,4), mean, na.rm = TRUE)
bias.q.md <- apply(sim.q.bias, c(2,3,4), median, na.rm = TRUE)
bias.q.bc <- apply(sim.q.bc, c(2,3,4), mean, na.rm = TRUE)

x.labels <- c("30","","50","","70","","90","", "150", "200", "300")
```

## Illustrate bias results

### Make function
```{r}
plot_bias_res <- function(data, pop.m, pop.md, nvec, nP, x.labels){
  df <- tibble(Bias = as.vector(data),
             Skewness = factor(rep(round(pop.m-pop.md), length(nvec)*9)),
             Size = rep(rep(nvec,each=nP), 9),
             q = factor(rep(seq(1,9), each=nP*length(nvec))))

# make plot
p <- ggplot(df) + theme_classic() +
  geom_line(aes(x=Size, y=Bias, colour = Skewness), size = 1) + 
  geom_abline(intercept=0, slope=0, colour="black") +
  scale_colour_viridis_d() +
  scale_x_continuous(breaks=nvec, labels = x.labels) +
  scale_y_continuous(breaks=seq(0,50,10)) +
  coord_cartesian(ylim=c(-5,50)) +
  theme(plot.title = element_text(size=22),
        axis.title.x = element_text(size = 18),
        axis.text.x = element_text(size = 14, colour="black"),
        axis.text.y = element_text(size = 16, colour="black"),
        axis.title.y = element_text(size = 18),
        legend.key.width = unit(1.5,"cm"),
        legend.position = "right",
        # legend.position = c(0.55,0.85),
        legend.direction = "vertical",
        legend.text=element_text(size=16),
        legend.title=element_text(size=18),
        strip.background=element_rect(fill="grey", colour="black"),
        strip.text=element_text(size=16, colour="white", face="bold")) +
  labs(x = "Sample size", y = "Bias") +
  # make thicker legend lines
  guides(colour = guide_legend(override.aes = list(size=3))) +
  facet_wrap( ~ q, ncol = 3)
p
}
```

```{r, fig.width = 12, fig.height = 7}
p <- plot_bias_res(bias.hd, pop.m, pop.md, nvec, nP, x.labels)
p <- p + ggtitle("HD mean bias") 
p
```

```{r, fig.width = 12, fig.height = 7}
p <- plot_bias_res(bias.q, pop.m, pop.md, nvec, nP, x.labels)
p <- p + ggtitle("QT8 mean bias") 
p
```

## Illustrate median bias results

```{r, fig.width = 12, fig.height = 7}
p <- plot_bias_res(bias.hd.md, pop.m, pop.md, nvec, nP, x.labels)
p <- p + ggtitle("HD median bias") 
p
```

```{r, fig.width = 12, fig.height = 7}
p <- plot_bias_res(bias.q.md, pop.m, pop.md, nvec, nP, x.labels)
p <- p + ggtitle("QT8 median bias") 
p
```

## Illustrate bias corrected bias results

```{r, fig.width = 12, fig.height = 7}
p <- plot_bias_res(bias.hd.bc, pop.m, pop.md, nvec, nP, x.labels)
p <- p + ggtitle("HD mean bias (BC)") 
p
```

```{r, fig.width = 12, fig.height = 7}
p <- plot_bias_res(bias.q.bc, pop.m, pop.md, nvec, nP, x.labels)
p <- p + ggtitle("QT8 mean bias (BC)") 
p
```
